\documentclass[letterpaper, 12pt]{article}
\usepackage{../config} 
\date{}

\begin{document}

\begin{center}
    {\Large \textbf{Scenarios}\par}
\end{center}
\medskip

\section*{Scenario 1: News Website (e.g. El Espectador, La Silla Vacía)}
\begin{itemize}
    \item \textbf{Headline Navigation}: Navigate between headlines and select specific news articles.
    \item \textbf{Scrolling}: Scroll through the main page and within an article.
    \item \textbf{Navigating Categories}: Move between sections like “World News”, “Technology” or “Health”.
\end{itemize}

\section*{Scenario 2: E-commerce Website (e.g., Mercado Libre)}
\begin{itemize}
    \item \textbf{Product Search}: Search for a specific product and select it from search results.
    \item \textbf{Filter and Sort Options}: Apply filters (e.g., price, brand) and sort results by price, ratings, or relevance.
    \item \textbf{Adding to Cart}: Select a product and add it to the cart using gaze or voice commands.
    \item \textbf{Product Details Navigation}: Scroll through product images and descriptions, and navigate to reviews.
\end{itemize}

\section*{Scenario 3: Streaming Service (e.g., YouTube)}
\begin{itemize}
    \item \textbf{Playing and Controlling Media}: Play, pause, adjust volume, and seek within media content.
    \item \textbf{Searching for Content}: Search for specific shows or videos.
    \item \textbf{Browsing Categories}: Navigate categories (e.g., “Recommended,” “Trending”).
    \item \textbf{Interacting with Video Elements}: Click on recommended videos and explore comments.
\end{itemize}


\section*{Scenario 4: Online Form/Survey (e.g., MBTI test)}
\begin{itemize}
    \item \textbf{Field Navigation}: Fill in multi-field forms (e.g., name, email) and move between fields.
    \item \textbf{Form Submission}: Complete and submit the form.
\end{itemize}


\section*{Scenario 5: Educational Website (e.g., Wikipedia, Coursera)}
\begin{itemize}
    \item \textbf{Navigating through Topics}: Navigate between sections within an article.
    \item \textbf{Following In-Article Links}: Click on hyperlinks within an article to view related topics.
\end{itemize}


\section*{Scenario 6: Knowledge Base or FAQ Site (e.g., Stack Overflow)}
\begin{itemize}
    \item \textbf{Searching for Help Topics}: Search for a specific help topic and select from the results.
    \item \textbf{Navigating Threads or Sections}: Open and explore different threads in an FAQ.
    \item \textbf{Interacting with Answer Elements}: Upvote answers, click code examples, or follow hyperlinks.
    \item \textbf{Scrolling through Long Answers}: Scroll through detailed answers and navigate back to the top.
\end{itemize}

\end{document}
